Manuscript 1 code

### 2024-10-25 manuscript_1_code.Rmd
fixed f5v3 aes
cleaned plot themes, re-did figure 1 without panel titles

## Figure formatting
```{r figure formatting info}
mytheme <- theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size=24), 
        plot.title = element_text(size = 24),
        panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))

@@

#THIS IS THE BIG CHANGE HERE: 9/19
filtered_data$habitat <- factor(filtered_data$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))

#DID NOT TOUCH BELOW:
not_algae <- c("ascidian", "bare_space", "coral", "coral_rubble", "corallimorpharia", "heteractis_sp", "millepora_platyphylla", "no_data", "sand", "sarcophyton_sp", "shell_debris", "soft_coral", "sponge", "tridacna_sp", "zooxanthellae", "row_sums")

algae <- filtered_data[ , -which(names(filtered_data) %in% not_algae)]

@@

# make er long
macro_long_data <- pivot_longer(
  data = macroalgae,
  cols = grep("acanthophora_spicifera", colnames(macroalgae)):grep("valonia_ventricosa", colnames(macroalgae)),
  names_to = "taxa",
  values_to = "percent_cover") %>% 
  mutate(prop_cover = percent_cover/100) %>% 
  select(-percent_cover)

@@

## plot
```{r figure 1, fig.height = 10, fig.width=14, warning=FALSE}
(figure_1 <- ggplot() +
  geom_point(data = figure_1_data, aes(x = year, y = percent_cover, colour = functional_group), size = 3) +
  geom_errorbar(data = figure_1_data, aes(x = year, ymin = percent_cover - se, ymax = percent_cover + se, colour = functional_group),
                width = 0, size = 1.3) +
   geom_line(data = figure_1_data, aes(x = year, y = percent_cover, colour = functional_group), linewidth = 1) +
  facet_wrap(~ habitat) +
  annotate("segment", x = 2006, xend = 2010, y = 75, yend = 75, linewidth = 2, colour = "grey") +
  scale_colour_manual(values = functional_group_colours) +
  # scale_fill_manual(values = functional_group_colours) +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(cover_long$year)) +
   labs(y = "Percent Cover \n",
        x = "Year") +
  theme_bw() + 
  mytheme)

# ggsave(filename = "output/figure_1.png", figure_1, height = 10, width = 14)
```

## plot after aes changes
```{r Figure 1 v2, fig.height = 10, fig.width=14}
plot_list <- lapply(levels(figure_1_data$habitat), function(hab) {
  ggplot(data = subset(figure_1_data, habitat == hab)) +
    geom_point(aes(x = year, y = percent_cover, colour = functional_group), size = 3) +
    geom_errorbar(aes(x = year, ymin = percent_cover - se, ymax = percent_cover + se, colour = functional_group), 
                  width = 0, size = 1.3) +
    geom_line(aes(x = year, y = percent_cover, colour = functional_group), linewidth = 1) +
    annotate("segment", x = 2006, xend = 2010, y = 75, yend = 75, linewidth = 2, colour = "grey") +
    geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
    geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
    scale_colour_manual(values = functional_group_colours) +
    scale_x_continuous(breaks = unique(figure_1_data$year)) +
    labs(y = "Percent Cover",
         x = "Year",
         title = hab) +  # Add habitat as title
    theme_bw() +
    mytheme
})

(figure_1 <- ggarrange(plotlist = plot_list, 
                      ncol = 2, nrow = 2, 
                      labels = c("a.", "b.", "c.", "d."),
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 24, color = "black", face = "plain")))
# 
# figure_1_caption <- "Figure 1. Benthic coverage of four major space holders in Moorea across four habitats (Fringing, Backreef, Forereef at 10m depth, Forereef  at 17m depth). Annual fluctuations in percent cover of macroalgae, coral, turf, and crustose coralline algae (CCA) are displayed as points for the average cover for each benthic group across sites at each habitat with lines showing standard error. Dotted lines show disturbance events for Cyclone Oli (2010) in black, and the 2019 bleaching event in red, and the gray horizontal line shows crown of thorns (COTs) outbreak which occurred from 2007-2010."
# 
# figure_1_with_caption <- annotate_figure(figure_1,
#                 bottom = text_grob(figure_1_caption, hjust = 0.5, vjust = 1, size = 10))

@@

### plot
```{r figure 2a}
(figure_2a <- ggplot() +
  geom_point(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
  geom_line(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = quad_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se,
                                             colour = habitat), width = 0, size = 1.3, position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  # scale_fill_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 2, yend = 2, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(quad_richness_df$year)) +
   labs(y = "Macroalgal Richness",
        x = "Year",
        title = "Quadrat-level Richness") +
  theme_bw() + 
  mytheme +
   theme(axis.text.x = element_text(size=20),
         axis.title.x = element_text(size=22),
         axis.title.y = element_text(size=22),
      axis.text.y = element_text(size=20),
      plot.title = element_text(size=24),
      legend.text = element_text(size=20),
      legend.title = element_blank()))

@@

### plot
```{r plot figure 2b}
(figure_2b <- ggplot() +
  geom_point(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
#  geom_jitter(data = alpha_diversity_site_macro, 
#  aes(x = year, y = richness, colour = habitat, alpha = 0.05), size = 2, width = 0.4, height = 0) +
  geom_line(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = site_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se, colour = habitat), size = 1.3, width = 0,  position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 12, yend = 12, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(site_richness_df$year)) +
   labs(y = "",
        x = "Year",
        title = "Site-level Richness") +
  mytheme +
   theme(axis.text.x = element_text(size=20),
         axis.title.x = element_text(size=22),
      axis.text.y = element_text(size=20),
      plot.title = element_text(size=24),
      legend.text = element_text(size=20),
      legend.title = element_blank(),
      ))

@@

```{r figure 3a plot}
(figure_3a <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.5) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# ggsave(filename = "output/figure_3a.png", figure_3a, height = 10, width = 14)
```

@@

```{r figure 3b plot}
(figure_3b <- 
  ggplot() +
  geom_point(data = functional_richness_quad_cover,
             aes(x = fg_richness_quad, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects_fg, aes(x = fg_richness_quad, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_fg, aes(x = fg_richness_quad, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r synchrony cover plot}
(figure_3c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_synch_cov_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_cov_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r plot figure 3d}
(figure_3d <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_site_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal Richness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# ggsave(filename = "output/figure_3d.png", figure_3d, height = 10, width = 14)
```

@@

```{r figure 3e plot }
(figure_3e <- 
  ggplot() +
  geom_point(data = functional_richness_site_cover,
             aes(x = fg_richness_site, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_fg_cover_effects, aes(x = fg_richness_site, y = inv_logit(yvar), colour = habitat),
            size = 1.5) +
  geom_ribbon(data = filtered_site_fg_cover_effects, aes(x = fg_richness_site, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "Functional Richness", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
#ggsave(filename = "output/figure_3e_v2.png", figure_3e, height = 10, width = 14)
```

@@

```{r synchrony cover plot site}
(figure_3f <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_cov_effects_site, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_cov_effects_site, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r figure 4a}
(figure_4a <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects, aes(x = richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r plot figure 4b}
(figure_4b <- 
  ggplot() +
  geom_point(data = fg_stability_quad_level,
             aes(x = fg_richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_stab_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)
```

@@

# ggsave(filename = "output/figure_5_option3.png", figure_5, height = 8, width = 16)
```

>>>>

## Figure formatting
```{r figure formatting info}
trends_theme <- theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_text(size=24), 
        plot.title = element_text(size = 24),
        panel.background = element_rect(fill = "white"), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))

model_themes <-   theme_bw() + 
  theme(axis.title.x = element_text(size=24), 
        axis.title.y = element_text(size=24), 
        axis.text.x = element_text(size=22), 
        axis.text.y = element_text(size=22),
        legend.text = element_text(size=22),
        plot.title = element_text(size=26), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend

@@

# re-factor for figures
filtered_data$habitat <- factor(filtered_data$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))

# note non-algae species
not_algae <- c("ascidian", "bare_space", "coral", "coral_rubble", "corallimorpharia", "heteractis_sp", "millepora_platyphylla", "no_data", "sand", "sarcophyton_sp", "shell_debris", "soft_coral", "sponge", "tridacna_sp", "zooxanthellae", "row_sums")

# remove
algae <- filtered_data[ , -which(names(filtered_data) %in% not_algae)]

@@

# make long dataset
macro_long_data <- pivot_longer(
  data = macroalgae,
  cols = grep("acanthophora_spicifera", colnames(macroalgae)):grep("valonia_ventricosa", colnames(macroalgae)),
  names_to = "taxa",
  values_to = "percent_cover") %>% 
  mutate(prop_cover = percent_cover/100) %>% 
  select(-percent_cover)

@@

## plot

```{r Figure 1, fig.height = 10, fig.width=14}
plot_list <- lapply(levels(figure_1_data$habitat), function(hab) {
  ggplot(data = subset(figure_1_data, habitat == hab)) +
    geom_point(aes(x = year, y = percent_cover, colour = functional_group), size = 3) +
    geom_errorbar(aes(x = year, ymin = percent_cover - se, ymax = percent_cover + se, colour = functional_group), 
                  width = 0, size = 1.3) +
    geom_line(aes(x = year, y = percent_cover, colour = functional_group), linewidth = 1) +
    annotate("segment", x = 2006, xend = 2010, y = 75, yend = 75, linewidth = 2, colour = "grey") +
    geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
    geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
    scale_colour_manual(values = functional_group_colours) +
    scale_x_continuous(breaks = unique(figure_1_data$year)) +
    labs(y = "Percent Cover",
         x = "Year", title = "") +  
    trends_theme
})

(figure_1 <- ggarrange(plotlist = plot_list, 
                      ncol = 2, nrow = 2, 
                      labels = c("a.", "b.", "c.", "d."),
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 24, color = "black", face = "plain")))

@@

### plot
```{r figure 2a}
(figure_2a <- ggplot() +
  geom_point(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
  geom_line(data = quad_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = quad_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se,
                                             colour = habitat), width = 0, size = 1.3, position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  # scale_fill_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 2, yend = 2, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(quad_richness_df$year)) +
   labs(y = "Macroalgal Richness",
        x = "Year",
        title = "Quadrat-level Richness") +
   trends_theme)

@@

### plot
```{r plot figure 2b}
(figure_2b <- ggplot() +
  geom_point(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), size = 4,
             position = position_dodge(0.4)) +
#  geom_jitter(data = alpha_diversity_site_macro, 
#  aes(x = year, y = richness, colour = habitat, alpha = 0.05), size = 2, width = 0.4, height = 0) +
  geom_line(data = site_richness_df, aes(x = year, y = richness_mean, colour = habitat), linewidth = 1) +
  geom_errorbar(data = site_richness_df, aes(x = year, ymin = richness_mean - richness_se, ymax = richness_mean + richness_se, colour = habitat), size = 1.3, width = 0,  position = position_dodge(0.4)) +
  scale_colour_manual(values = habitat_colours) +
  #geom_segment(aes(y = 75, yend = 75, x = 2006, xend = 2010), linewidth = 2, colour = "grey") +
  annotate("segment", x = 2006, xend = 2010, y = 12, yend = 12, linewidth = 2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 1) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 1) +
   scale_x_continuous(breaks = unique(site_richness_df$year)) +
   labs(y = "",
        x = "Year",
        title = "Site-level Richness") +
  trends_theme)

@@

```{r figure 3a plot}
(figure_3a <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.5) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "", title = "") +
  model_themes 
         )
# ggsave(filename = "output/figure_3a.png", figure_3a, height = 10, width = 14)
```

@@

```{r figure 3b plot}
(figure_3b <- 
  ggplot() +
  geom_point(data = functional_richness_quad_cover,
             aes(x = fg_richness_quad, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects_fg, aes(x = fg_richness_quad, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_fg, aes(x = fg_richness_quad, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )

@@

```{r synchrony cover plot}
(figure_3c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_synch_cov_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_cov_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  trends_theme
         )

@@

```{r plot figure 3d}
(figure_3d <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_site_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal Richness", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_3d.png", figure_3d, height = 10, width = 14)
```

@@

```{r figure 3e plot }
(figure_3e <- 
  ggplot() +
  geom_point(data = functional_richness_site_cover,
             aes(x = fg_richness_site, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_fg_cover_effects, aes(x = fg_richness_site, y = inv_logit(yvar), colour = habitat),
            size = 1.5) +
  geom_ribbon(data = filtered_site_fg_cover_effects, aes(x = fg_richness_site, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "Functional Richness", title = "") +
  trends_theme
         )
#ggsave(filename = "output/figure_3e_v2.png", figure_3e, height = 10, width = 14)
```

@@

```{r synchrony cover plot site}
(figure_3f <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony_site,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_cov_effects_site, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_cov_effects_site, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "", title = "") +
  trends_theme
         )

@@

```{r figure 4a}
(figure_4a <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects, aes(x = richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "", title = "") +
  trends_theme
         )

@@

```{r plot figure 4b}
(figure_4b <- 
  ggplot() +
  geom_point(data = fg_stability_quad_level,
             aes(x = fg_richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_fg, aes(x = fg_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_stab_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)
```

@@

# ggsave(filename = "output/figure_5_option3.png", figure_5, height = 6, width = 22)
```
